---
title: "Grad School Admission"
Author: "Juliet Thistleton"
output: html_notebook
---


# Install packages (if you do not have already)

```{r}
# install.packages("rmarkdown")
# install.packages("janitor")
# install.packages("broom")
```

# Load Packages

```{r}
library(janitor)
library(broom)
library(rmarkdown)
```


# Load Data 

```{r}
setwd(getwd())
df1 <- read.csv(("Admission_Predict_Ver1.1.csv")) |> clean_names()
```

# Putting each variable of the data frame into its own variable. 

```{r}
gre <- df1$gre_score
toefl <- df1$toefl_score
rating <- df1$university_rating
sop <- df1$sop
lor <- df1$lor
cgpa <- df1$cgpa
chance_admit <- df1$chance_of_admit
txt_cor <- "Correlationn Coefficient:"
txt_linear <- "Linear Regession Line:"

```


# Influence of Gre Scores on Admission Chances
```{r}
plot(x= gre, y = chance_admit, xlab = "Gre Scores", ylab = "Chance of Admission", main = "Gre Score's Correlation with Chance of Admission")
gre_lm <- lm(chance_of_admit ~gre_score, data = df1)
abline(gre_lm)
tidy(summary(gre_lm))

cat(txt_cor, cor(gre,chance_admit))
cat("\n", txt_linear, "y = -2.48 + 0.01x")
```


# Influence of Toefl on Admission Chances

```{r}
plot(toefl, chance_admit, xlab = "Toefl Score", ylab = "Chance of Admission") 
title(main = "Toefl Score's correlation with Chance of Admission")
toefl_lm <- lm(chance_of_admit ~toefl_score, data = df1)
abline(toefl_lm)
tidy(summary(toefl_lm))

cat(txt_cor, cor(toefl, chance_admit))
cat("\n", txt_linear, "y = -1.45 + 0.02x")

```

# Influence of University Rating on Admission Chances
```{r}
plot(rating, chance_admit, xlab = "University Rating Score", ylab = "Chance of Admission") 
title(main = "University Rating's Correlation with Chance of Admission")
rating_lm <- lm(chance_of_admit ~university_rating, data = df1)
abline(rating_lm)
tidy(summary(rating_lm))

cat(txt_cor, cor(rating, chance_admit))
cat("\n", txt_linear, "y = 0.46 + 0.09x")

```

# Influence of Statement of Purpose on Admission Chances
```{r}
plot(sop, chance_admit, xlab = "SOP Score", ylab = "Chance of Admission") 
title(main = "SOP Score's correlation with Chance of Admission")
sop_lm <- lm(chance_of_admit ~sop, data = df1)
abline(sop_lm)
tidy(summary(sop_lm))

cat(txt_cor, cor(sop, chance_admit))
cat("\n", txt_linear, "y = 0.39 + 0.10x")

```

# Influence of Letter of Recommendation on Admission Chances
```{r}
plot(lor, chance_admit, xlab = "LOR Score", ylab = "Chance of Admission") 
title(main = "LOR Score's correlation with Chance of Admission")
lor_lm <- lm(chance_of_admit ~lor, data = df1)
abline(lor_lm)
tidy(summary(lor_lm))

cat(txt_cor, cor(lor, chance_admit))
cat("\n", txt_linear, "y = 0.38 + 0.10x")


```

# Influence of CGPA on Admission Chances
```{r}
plot(cgpa, chance_admit, xlab = "CGA Score", ylab = "Chance of Admission") 
title(main = "CGPA Score's correlation with Chance of Admission")
cgpa_lm <- lm(chance_of_admit ~cgpa, data = df1)
abline(cgpa_lm)
tidy(summary(cgpa_lm))

cat(txt_cor, cor(cgpa, chance_admit))
cat("\n", txt_linear, "y = -1.04 + 0.21x")


```
# Creating a data frame of only the top 24% of the 500 who had the highest chances of getting into UCLA 

```{r}
df2 = df1 |>
  mutate(gpa = cgpa *0.4) |>
  select(serial_no, gre_score, toefl_score, university_rating, sop, lor, cgpa, gpa, research, chance_of_admit) 
  
df2 = df2[order(-chance_admit),]



df2 = df2[1:124,]  

mean(df2$gpa)

gpa_adj_lm = lm(df2$chance_of_admit ~gpa, data = df2)
tidy(summary(gpa_adj_lm))
sd(df2$gpa)


```


# GPA

Null Hypothesis: mu = 3.80

Alternative: mu != 3.80

Alpha level = 0.05

Rejection region: (-infinity, -1.645]

```{r}
xbar = 3.733
h0 = 3.800
s = 0.1089738
n = 500

z =((xbar - h0) / (s/sqrt(n)))
cat("TS Observed:",z)
```
